---
title: 'Interactive Illustration of Learning Rates'
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
#library(dplyr)
library(ggplot2)
#library(forcats)
library(shiny)
library(tidyverse)
library(plotly)
theme_set(theme_light())
# # Data cleaning and processing
# yields_tidy <- readRDS("yields_tidy.rds")
# top_crops <- yields_tidy %>%
#   count(crop, sort = TRUE) %>%
#   head(9) %>%
#   pull(crop)
```

```{r}
plot_lr <- function(ntrials, start, end, sd, lr) {
  # Defining variables
  # ntrials <- ntrials # Number of trials
  # start <- start # Start guess
  # end <- end # True value
  # sd <- sd # Standard deviation
  # lr <- lr # Learning rates

  # Useful calculation
  len <- as.numeric(length(lr))

  # Making the dataframe
  EV <- matrix(0, ncol = 2, nrow = ntrials * len)  %>% data.frame()
  colnames(EV)[1] <- 'LR'
  colnames(EV)[2] <- 'EV'

  x <- rnorm(ntrials, end, sd)

  for (i in 1:len){
    EV[1 + (i - 1) * ntrials, 2] <- start
  
    EV[1 + (i - 1) * ntrials, 1] <- paste('LR', lr[i], sep = '_')
  }


  EV$Trials <- 1:ntrials


  for (i in 1:len) {
    for (t in 2:ntrials) {
      tx <- t
      t <- t + (i - 1) * ntrials
    
      EV[t, 1] <- paste('LR', lr[i], sep = '_')
    
      EV[t, 2] <- EV[t - 1, 2] + lr[i] * (x[tx] - EV[t - 1, 2])
    }
    tx <- 2
  }

  g <- EV %>% 
   ggplot(aes(x = Trials, y = EV, color = LR)) +
   geom_line() +
    xlab('Trial') +
    facet_wrap(~ LR) +
    geom_hline(aes(yintercept = end), linetype = 'dotted', alpha = 0.5) +
    theme_classic() %>% ggplotly()
  
  return(g)
}

```


```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("num_trials",
              label = "Number of Trials:",
              choices = seq(100,1000,10),
              selected = 100,
              selectize = TRUE,
              multiple = FALSE),
  selectInput("start_guess",
              label = "Start Guess:",
              choices = seq(10,1000,10),
              selected = 30,
              selectize = TRUE,
              multiple = FALSE),
  selectInput("end_guess",
              label = "Value for Guessing:",
              choices = seq(10,1000,10),
              selected = 30,
              selectize = TRUE,
              multiple = FALSE),
  selectInput("stand_divi",
              label = "Standard deviation:",
              choices = seq(10,100,5),
              selected = 10,
              selectize = TRUE,
              multiple = FALSE),
  selectInput("learn",
              label = "Learning Rate:",
              choices = seq(0,1,0.0001),
              selected = c(0.1, 0.01, 0.001),
              selectize = TRUE,
              multiple = TRUE)
  # radioButtons("facet_scales",
  #              label = "",
  #              choices = c("Free y-axis" = "free_y",
  #                          "Shared y-axis" = "fixed"))
)
renderPlotly({
    plot_lr(ntrials = input$num_trials, 
            start = input$start_guess, 
            end = input$end_guess, 
            sd = input$stand_divi, 
            lr = c(input$learn))
  # yields_tidy %>%
  #   filter(entity %in% input$entity,
  #          crop %in% input$crop) %>%
  #   plot_yields(facet_scales = input$facet_scales)
})
